### 2019-06-12 doc/chapters/towards_verifying_addition.tex
explain more

This is an easy to fix.
We just extract the private class out of the object.
This is not exactly the same code but since the class is still private it can not be extended outside of the file.

@@

Seems like Stainless does not support the second string parameter of require or at least it throws a warning about it.
We can safely remove it.

@@

This error is hard to understand, but we can see that there is a missing Long to BigInt conversion.
So we search for all longs in the code.
\begin{lstlisting}[language=scala]
  private case class Int64Impl(underlying: BigInt) extends Int64 {
    require(underlying >= -9223372036854775808L)
    require(underlying <= 9223372036854775807L)
  }
\end{lstlisting}

Looks like it can not compare a BigInt with a Long value.
We can easily convert this Long value to a BigInt with string literals parameter.

@@

This show, that there is an invalid specification in checkResult and Stainless prints a counter example for it.

Let's ignore this for a moment and write the verification for our addition with zero.

>>>>

This is easy to fix.
We just extract the private class out of the object.
This is not exactly the same code, because other classes in the same file could now access the private class.
But for our property it does not change anything.

@@

Seems like Stainless does not support the second string parameter of require or at least it throws a warning about it.
We can safely remove the string parameters from the requires, since they only serve as error message.

@@

This error is hard to understand, but we can see that there is a missing Long to BigInt conversion.
So we search for all Long values in the code.
\begin{lstlisting}[language=scala]
  private case class Int64Impl(underlying: BigInt) extends Int64 {
    require(underlying >= -9223372036854775808L)
    require(underlying <= 9223372036854775807L)
  }
\end{lstlisting}

Looks like it can not compare a BigInt with a Long value.
We can easily convert this Long value to a BigInt with string literal parameter by passing this numbers as strings to the BigInt constructor.

@@

This show, that there is an invalid specification in checkResult and Stainless prints a counterexample for it.

Let's ignore this for a moment and write the specification for the \nameref{property_2}.
